CTFEF

### 2023-08-28 Papers/FEDCIS-2023-presentation/sections/CTFEF.tex
some more presentation stuff

    \begin{itemize}
        \item Translates source code into Intermidiate Representation\begin{itemize}
            \item Parse
            \item Validate syntax
            \item Inline operators with special syntax (ex: \lstinline|typeof|)
        \end{itemize}
        \item 
    \end{itemize}

@@

>>>>

    \begin{itemize}
        \item Translates source code into Intermidiate Representation\begin{itemize}
            \item Parse
            \item Validate syntax
            \item Inline operators with special syntax (ex: \lstinline|typeof|)
        \end{itemize}
        \item Processes user code and Compiler Interface\begin{itemize}
            \item Compiler interface translates user code into backend Intermidiate Representation
        \end{itemize}
        \item May perform additional processing\begin{itemize}
            \item In C-=-1 it invokes the interpreter to execute metaprogramming code
        \end{itemize}
    \end{itemize}

@@

\begin{frame}
    \frametitle{Intermidiate Representation}

    \begin{itemize}
        \item Complete representation of the user program
        \item Simplified form of the compiled language\begin{itemize}
            \item Resolved function overloads
            \item Advanced constructs lowered to basic ones (foreach loops transformed into while)
        \end{itemize}
        \item Stored using Interpreter data structures in compiler memory\begin{itemize}
            \item 
        \end{itemize}
    \end{itemize}

\begin{frame}
    \frametitle{Interpreter}

    \begin{itemize}
        \item Operates on Intermidiate Representation
    \end{itemize}
